---
title: "ggplot"
author: "Haya Abuzuluf 32601130"
date: '2018-04-08'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#load library  

```{r}
library(tidyverse)
source("https://bioconductor.org/biocLite.R")
biocLite("phyloseq")
library(phyloseq)
```

#Read in a table.
```{r}
#read.table(file="Saanich.metadata.txt")
#read.table(file="Saanich.metadata.txt", header=TRUE, row.names=1, sep="\t", na.strings="NAN")
metadata = read.table(file="Saanich.metadata.txt", header=TRUE, row.names=1, sep="\t")
#Read in a table.
#read.table(file="Saanich.OTU.txt")
metadata %>% 
  select(O2_uM)
metadata %>% 
  select(matches("O2|oxygen"))
metadata %>% 
  filter(O2_uM == 0)
metadata %>% 
  filter(O2_uM == 0) %>% 
  select(Depth_m)
metadata %>% 
  mutate(N2O_uM = N2O_nM/1000)
metadata %>% 
  transmute(N2O_uM = N2O_nM/1000)
metadata %>% 
  mutate(N2O_uM = N2O_nM/1000) %>% 
  ggplot() + geom_point(aes(x=Depth_m, y=N2O_uM))

```


#read table  
```{r}
load("phyloseq_object.RData")
```

#graph metadata, plot depth by oxygen  
```{r}
ggplot(metadata, aes(x=O2_uM, y=Depth_m))
```
#use point plot  
```{r}
ggplot(metadata, aes(x=O2_uM, y=Depth_m)) +
  geom_point()
```

#change color of dots to blue   
```{r}
ggplot(metadata, aes(x=O2_uM, y=Depth_m, color="blue")) +
  geom_point()
```

#change color within geom function  
```{r}
ggplot(metadata, aes(x=O2_uM, y=Depth_m)) +
  geom_point(color="blue")
```

#change chape and size  
```{r}
ggplot(metadata, aes(x=O2_uM, y=Depth_m, size=OxygenSBE_V)) +
  geom_point()
```

#Exercise 1: Depth against PO4 concentration  
```{r}
ggplot(metadata, aes(x=PO4_uM, y=Depth_m)) +
  geom_point(shape=24) +
  geom_point(color="purple")
```

#Exercise 2: using dplyr plot temperature in Fahrenheit against depth  
###plot in Celcius  
```{r}
ggplot(metadata, aes(x=Temperature_C, y=Depth_m)) +
  geom_point() +
  geom_point(color="purple")
```

###use dplyr function mutate to covert to Fahrenheit  
```{r}
metadata %>% 
  mutate(Temperature_F = Temperature_C*1.8+32) %>% 
  ggplot() + geom_point(aes(x=Temperature_F, y=Depth_m),color="purple")
```

#ggplot with phyloseq  
```{r}
physeq
```

#plot phylum level communities by depth by filling the fill  
```{r}
plot_bar(physeq, fill="Phylum")
```

#calculate percentage of total of each sample for each OTU  
```{r}
physeq_percent = transform_sample_counts(physeq, function(x) 100 * x/sum(x))
```

#plot the phyla percentage  
```{r}
plot_bar(physeq_percent, fill="Phylum")
```

#specify identity to remove black lines  
```{r}
plot_bar(physeq_percent, fill="Phylum") + 
  geom_bar(aes(fill=Phylum), stat="identity")
```

#Exercise 3: bar plot  
```{r}
plot_bar(physeq_percent, fill="Genus") + 
  geom_bar(aes(fill=Genus), stat="identity") +
  labs(x = "Sample Depth", y = "Percent relative abundance",
       title ="Genera from 10 to 200 m in Saanich Inlet")
```

#Faceting: separates data into multiple panels to see patterns more clearly   
```{r}
plot_bar(physeq_percent, fill="Phylum") +
  geom_bar(aes(fill=Phylum), stat="identity") +
  facet_wrap(~Phylum)
```

#remove legend because each facet has a label  
```{r}
plot_bar(physeq_percent, fill="Phylum") +
  geom_bar(aes(fill=Phylum), stat="identity") +
  facet_wrap(~Phylum, scales="free_y") +
  theme(legend.position="none")
```


#Exercise 4: nutrient concentrations in uM for O2, PO4, SiO2, NO3 and NO2 by depth  
```{r}
gather2= gather(metadata, nutrients, uM, NH4_uM, NO3_uM, O2_uM, PO4_uM, SiO2_uM, NO2_uM)

ggplot(gather2, aes(x=Depth_m, y=uM, color="blue")) +
  facet_wrap(~nutrients, scales="free_y") +
  geom_point() + geom_line() +
  theme(legend.position="none")

```
